Another paper with lots of text and fancy pictures

### 2023-12-01 paper.tex
Remake plots

The test was performed by firstly evaluating the inequation in a cube
$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
$F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
pixels wide image as the input. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
farther than 0.1 (20 pixels) from curves of discontinuity (look at
\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell.png}
    \label{fig:sss-dumbbell}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-err.png}
    \label{fig:sss-dumbbell-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
    II discontinuity) at curves A, B and C.]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-precise.png}
    \label{fig:sss-dumbbell-precise}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}

>>>>

The test is performed by firstly evaluating the inequation in a cube
$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
$F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
pixels wide image as the input. $F_{sss}$ function is evaluated in $XY$
plane. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
farther than 0.1 (20 pixels) from curves of discontinuity (look at
\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell.png}
    \label{fig:sss-dumbbell}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-err.png}
    \label{fig:sss-dumbbell-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
    II discontinuity) at curves A, B and C.]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-precise.png}
    \label{fig:sss-dumbbell-precise}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}
